<<echo=FALSE, cache=FALSE>>=
set_parent('./project.Rnw')
@
\section{Dataset}
\label{sec:Dataset}
\todo{New chapter here}
\colorbox{yellow}{Need to write something about the data set. Description and so on.}\\
\colorbox{yellow}{Look at what others have done.} \\
\url{http://sci2s.ugr.es/keel/dataset.php?cod=109} Spam data.\\

\section{Boosting}
\label{sec:SimBoosting}
Need to to simulations of boosting.
\subsection{AdaBoost}
\label{sub:SimAdaBoost}
\colorbox{yellow}{Need to look into the use of bootstrap samples, as they do better in the simulations.} 
\\ \colorbox{yellow}{Show difference between using weak and strong classifiers.}\\
\\
Simulation 1: \\
Chose, 4 or 5 different amount of depths of trees used. Plot test error as function of boosting iterations.\\
\\
Simulation 2: \\
With and without bootstraping. Maybe include this in Simulation 1.

\subsection{Gradient boosting}
\label{sub:SimGradBoost}
\colorbox{yellow}{Both gradient and stochastic.}\\
\colorbox{yellow}{Problems with gbm. See tutorial}
\url{https://vimeo.com/71992876} \\
\url{http://www.datarobot.com/blog/r-getting-started-with-data-science/}
\\ \colorbox{yellow}{Should I include offset in the model?}
\\ \colorbox{yellow}{Make adaboost with gbm as good as with adabag}
\\ \colorbox{yellow}{Use gbm.fit, as it should be faster for ''power users''} \\
\url{http://www.saedsayad.com/docs/gbm2.pdf} \colorbox{yellow}{Guide to gbm package}\\
\\
Simulation 1:\\
Plot error as function of iterations. This should be done for different shrinkage parameters.\\
Consider plotting training error as well.\\
\\
Simulation 2:\\
Plot error as function of iterations, for different \verb+bag.fractions+, and report time for the different baggigs.\\
\\
Simulation 3:\\
Use \verb+interaction.depth+ (nr of splits) to set depth of tree, and see how that affect error as function of nr of iteratoins/trees.\\
\colorbox{yellow}{Maybe use carot to tune mode to see how good it is?}\\
\url{http://topepo.github.io/caret/training.html}





\subsection{Bagging and Random Forest}
\label{sub:BaggandRFSim}
Simulation 1: \\
Do simulations for bagging with different bootstrap sizes.\\
\\
Simulation 2: \\
\\
Maybe together with bagging, do simulations for as function of $m$'s, for different bootstrap sizes? \\
\colorbox{yellow}{Not sure what is best here.}





\section{Compare methods}
\label{sec:Compare methods}
\colorbox{yellow}{Show CART here as well.}

\subsection{Robustness}
\label{sub:Robustness}

\colorbox{yellow}{Add noise to previous test and see how stable the results are.}
